Figures

### 2016-08-16 case_study_ohi/ohi_single_datasets.Rmd
cleaning out old plots; updating figures; editing manuscript

### get spp_info - git-annex original
ohi_spp_info <- read_csv(file.path(dir_anx, 'v2016/int/spp_all_cleaned.csv')) %>%
  filter(!is.na(cat_score))  %>% ### filter out unassessed and DD species
  filter(!is.na(spatial_source)) ### filter out unmapped species

@@

iucn_spp_cells <- read_csv(file.path(dir_anx, 'v2016/int/iucn_cells_spp.csv'),
                           col_types = 'cddddc') %>%
  filter(presence != 5) %>%
  filter(iucn_sid %in% ohi_spp_info$iucn_sid) %>%
  filter(loiczid %in% ohi_rgn_cells$loiczid)

### NOTE: by using the 2016 cell files we're also getting the BOTW species...
### either mention in methods, or filter out!!!

@@

### bind IUCN loiczid dataframe to species risk category dataframe
iucn_spp_cells <- iucn_spp_cells %>%
  left_join(ohi_spp_info %>% select(iucn_sid, cat_score),
            by = 'iucn_sid')

### group by loiczid, then summarize to find means (and counts)
iucn_cell_sums <- iucn_spp_cells %>%
  filter(!is.na(cat_score)) %>%
  group_by(loiczid) %>%
  summarize(mean_cat = mean(cat_score),
            n_spp    = n())

write_csv(iucn_cell_sums, file.path(dir_git, 'case_study_ohi/iucn_spp_cell_sums.csv'))

### bind cells to regions dataframe and summarize
iucn_rgn_sums <- iucn_cell_sums %>%
  inner_join(ohi_rgn_cells,
             by = 'loiczid') %>%
  # mutate(rgn_area = cell_area * proportionArea,
  #        area_weighted_mean_cat   = weighted_mean_cat   * rgn_area,
  #        area_weighted_mean_trend = weighted_mean_trend * rgn_area) %>%
  mutate(cell_area_weight = cell_area * n_spp * proportionArea,
         area_weighted_mean_cat = mean_cat * cell_area_weight) %>%
  arrange(loiczid)

iucn_rgn_sums <- iucn_rgn_sums %>%
  group_by(rgn_id) %>%
  summarize(rgn_mean_cat = sum(area_weighted_mean_cat)/sum(cell_area_weight))

iucn_rgn_sums <- iucn_rgn_sums %>%
  mutate(status = 100 * ((1 - rgn_mean_cat) - 0.25) / 0.75)

write_csv(iucn_rgn_sums, file.path(dir_git, 'case_study_ohi/iucn_spp_region_sums.csv'))

@@

### group by loiczid, then summarize to find means (and counts)
am_cell_sums <- am_spp_cells %>%
  filter(!is.na(cat_score)) %>%
  group_by(loiczid) %>%
  summarize(mean_cat = mean(cat_score),
            n_spp    = n())

write_csv(am_cell_sums, file.path(dir_git, 'case_study_ohi/am_spp_cell_sums.csv'))

### bind cells to regions dataframe and summarize
am_rgn_sums <- am_cell_sums %>%
  inner_join(ohi_rgn_cells,
             by = 'loiczid') %>%
  # mutate(rgn_area = cell_area * proportionArea,
  #        area_weighted_mean_cat   = weighted_mean_cat   * rgn_area,
  #        area_weighted_mean_trend = weighted_mean_trend * rgn_area) %>%
  mutate(cell_area_weight = cell_area * n_spp * proportionArea,
         area_weighted_mean_cat = mean_cat   * cell_area_weight) %>%
  arrange(loiczid)

am_rgn_sums <- am_rgn_sums %>%
  group_by(rgn_id) %>%
  summarize(rgn_mean_cat = sum(area_weighted_mean_cat)/sum(cell_area_weight))

am_rgn_sums <- am_rgn_sums %>%
  mutate(status = 100 * ((1 - rgn_mean_cat) - 0.25) / 0.75)

write_csv(am_rgn_sums, file.path(dir_git, 'case_study_ohi/am_spp_region_sums.csv'))

@@

### DO THIS TO SANITY CHECK/SIMPLIFY IN SAME MANNER AS OTHERS???  REMOVE BOTW SPECIES???

### bind IUCN loiczid dataframe to species risk category dataframe
### Already done in above code chunk!
# am_spp_cells <- am_spp_cells %>%
#   left_join(ohi_spp_info %>% select(am_sid, cat_score = category_score),
#             by = 'am_sid')

ohi_am_maps <- ohi_spp_info %>%
  filter(str_detect(spatial_source, 'am'))

### bind cells to regions dataframe and summarize
am_rgn_sums <- am_cell_sum %>%
  inner_join(ohi_rgn_cells,
             by = 'loiczid') %>%
  # mutate(rgn_area = cell_area * proportionArea,
  #        area_weighted_mean_cat   = weighted_mean_cat   * rgn_area,
  #        area_weighted_mean_trend = weighted_mean_trend * rgn_area) %>%
  mutate(cell_area_weight = cell_area * n_spp * proportionArea,
         area_weighted_mean_cat = mean_cat   * cell_area_weight) %>%
  arrange(loiczid)

am_rgn_sums <- am_rgn_sums %>%
  group_by(rgn_id) %>%
  summarize(rgn_mean_cat = sum(area_weighted_mean_cat)/sum(cell_area_weight))

am_rgn_sums <- am_rgn_sums %>%
  mutate(status = 100 * ((1 - rgn_mean_cat) - 0.25) / 0.75)

write_csv(am_rgn_sums, file.path(dir_git, 'case_study_ohi/am_spp_region_sums.csv'))

@@

iucn_rgn_sums  <- read_csv(file.path(dir_git, 'case_study_ohi/iucn_spp_region_sums.csv'))
am_rgn_sums    <- read_csv(file.path(dir_git, 'case_study_ohi/am_spp_region_sums.csv'))
ohi_rgn_sums   <- read_csv(file.path('~/github/ohiprep/globalprep', 
                                     'spp_ico/v2016/output/spp_status_global.csv'))

status_df <- ohi_rgn_sums %>%
  select(rgn_id, ohi_st = score) %>%
  mutate(ohi_st = 100 * ohi_st) %>%
  full_join(am_rgn_sums %>% select(rgn_id, am_st = status), by = 'rgn_id') %>%
  full_join(iucn_rgn_sums %>% select(rgn_id, iucn_st = status), by = 'rgn_id') %>%
  mutate(diff_am   = am_st - ohi_st ,
         diff_iucn = iucn_st - ohi_st) %>%
  gather(scenario, diff, diff_am:diff_iucn)

@@

  geom_hline(yintercept = 0, color = 'gray50', size = .5) +
  geom_violin(fill = 'grey80', alpha = .5,
              scale = 'width',
              draw_quantiles = c(.25, .5, .75)) +
  geom_point(position = position_jitter(w = .3), 
             color = 'black', alpha = 1, size = 0.25) +
  geom_violin(fill = NA, 
              draw_quantiles = c(.25, .5, .75),
              scale = 'width') +
  labs(x = 'Scenario',
       y = 'Change in SPP status') +
  scale_x_discrete(labels = c('1. AquaMaps only', 
                              '2. IUCN only'))

>>>>

### get spp_info - git-annex original; modify spp info to exclude BOTW
ohi_spp_info <- read_csv(file.path(dir_anx, 'v2016/int/spp_all_cleaned.csv')) %>%
  filter(!is.na(cat_score))      %>% ### filter out unassessed and DD species
  filter(!is.na(spatial_source)) %>% ### filter out unmapped species
  mutate(spatial_source = ifelse(!is.na(am_sid) & spatial_source == 'iucn-bli', 'am', spatial_source)) %>%
  filter(spatial_source != 'iucn-bli')

@@

iucn_spp_cells <- read_csv(file.path(dir_anx, 'v2016/int/iucn_cells_spp.csv'),
                           col_types = 'cddddc') %>%
  filter(presence != 5) %>%
  filter(iucn_sid %in% ohi_spp_info$iucn_sid) %>%
  filter(loiczid %in% ohi_rgn_cells$loiczid)
### bind IUCN loiczid dataframe to species risk category dataframe
iucn_spp_cells <- iucn_spp_cells %>%
  left_join(ohi_spp_info %>% select(iucn_sid, cat_score),
            by = 'iucn_sid')

@@

### group by loiczid, then summarize to find means (and counts)
iucn_cell_sum <- iucn_spp_cells %>%
  filter(!is.na(cat_score)) %>%
  group_by(loiczid) %>%
  summarize(mean_cat = mean(cat_score),
            n_spp    = n())

write_csv(iucn_cell_sum, file.path(dir_git, 'case_study_ohi/iucn_spp_cell_sum.csv'))

### bind cells to regions dataframe and summarize
iucn_rgn_sum <- iucn_cell_sum %>%
  inner_join(ohi_rgn_cells,
             by = 'loiczid') %>%
  # mutate(rgn_area = cell_area * proportionArea,
  #        area_weighted_mean_cat   = weighted_mean_cat   * rgn_area,
  #        area_weighted_mean_trend = weighted_mean_trend * rgn_area) %>%
  mutate(cell_area_weight = cell_area * n_spp * proportionArea,
         area_weighted_mean_cat = mean_cat * cell_area_weight) %>%
  arrange(loiczid)

iucn_rgn_sum <- iucn_rgn_sum %>%
  group_by(rgn_id) %>%
  summarize(rgn_mean_cat = sum(area_weighted_mean_cat)/sum(cell_area_weight),
            mean_n_spp = mean(n_spp))

iucn_rgn_sum <- iucn_rgn_sum %>%
  mutate(status = 100 * ((1 - rgn_mean_cat) - 0.25) / 0.75)

write_csv(iucn_rgn_sum, file.path(dir_git, 'case_study_ohi/iucn_spp_region_sum.csv'))

@@

### bind cells to regions dataframe and summarize
am_rgn_sum <- am_cell_sum %>%
  inner_join(ohi_rgn_cells,
             by = 'loiczid') %>%
  # mutate(rgn_area = cell_area * proportionArea,
  #        area_weighted_mean_cat   = weighted_mean_cat   * rgn_area,
  #        area_weighted_mean_trend = weighted_mean_trend * rgn_area) %>%
  mutate(cell_area_weight = cell_area * n_spp * proportionArea,
         area_weighted_mean_cat = mean_cat   * cell_area_weight) %>%
  arrange(loiczid)

am_rgn_sum <- am_rgn_sum %>%
  group_by(rgn_id) %>%
  summarize(rgn_mean_cat = sum(area_weighted_mean_cat)/sum(cell_area_weight),
            mean_n_spp = mean(n_spp))

am_rgn_sum <- am_rgn_sum %>%
  mutate(status = 100 * ((1 - rgn_mean_cat) - 0.25) / 0.75)

write_csv(am_rgn_sum, file.path(dir_git, 'case_study_ohi/am_spp_region_sum.csv'))

@@

### get AM spp cells for combined scores
spp_ohi_am <- ohi_spp_info %>% 
  filter(str_detect(spatial_source, 'am'))

am_cell_sum_both <- am_spp_cells %>%
  filter(am_sid %in% spp_ohi_am$am_sid) %>%
  filter(!is.na(cat_score)) %>%
  group_by(loiczid) %>%
  summarize(mean_cat = mean(cat_score),
            n_spp    = n(),
            data     = 'am')

### get IUCN spp cells for combined scores
spp_ohi_iucn <- ohi_spp_info %>% 
  filter(str_detect(spatial_source, 'iucn'))

iucn_cell_sum_both <- iucn_spp_cells %>%
  filter(iucn_sid %in% spp_ohi_iucn$iucn_sid) %>%
  filter(!is.na(cat_score)) %>%
  group_by(loiczid) %>%
  summarize(mean_cat = mean(cat_score),
            n_spp    = n(),
            data     = 'iucn')

### Stick IUCN and AM together and find spp-weighted mean category
ohi_cell_sum <- iucn_cell_sum_both %>%
  bind_rows(am_cell_sum_both) %>%
  mutate(mean_weight_cat = mean_cat * n_spp) %>%
  group_by(loiczid) %>%
  summarize(mean_cat = sum(mean_weight_cat, na.rm = TRUE) / sum(n_spp, na.rm = TRUE),
            n_spp = sum(n_spp, na.rm = TRUE))

write_csv(ohi_cell_sum, file.path(dir_git, 'case_study_ohi/ohi_cell_sum.csv'))

### bind cells to regions dataframe and summarize by region
ohi_rgn_sum <- ohi_cell_sum %>%
  inner_join(ohi_rgn_cells,
             by = 'loiczid') %>%
  # mutate(rgn_area = cell_area * proportionArea,
  #        area_weighted_mean_cat   = weighted_mean_cat   * rgn_area,
  #        area_weighted_mean_trend = weighted_mean_trend * rgn_area) %>%
  mutate(cell_area_weight = cell_area * n_spp * proportionArea,
         area_weighted_mean_cat = mean_cat   * cell_area_weight) %>%
  arrange(loiczid)

ohi_rgn_sum <- ohi_rgn_sum %>%
  group_by(rgn_id) %>%
  summarize(rgn_mean_cat = sum(area_weighted_mean_cat)/sum(cell_area_weight),
            mean_n_spp = mean(n_spp))

ohi_rgn_sum <- ohi_rgn_sum %>%
  mutate(status = 100 * ((1 - rgn_mean_cat) - 0.25) / 0.75)

write_csv(ohi_rgn_sum, file.path(dir_git, 'case_study_ohi/ohi_spp_region_sum.csv'))

@@

iucn_rgn_sum  <- read_csv(file.path(dir_git, 'case_study_ohi/iucn_spp_region_sum.csv'))
am_rgn_sum    <- read_csv(file.path(dir_git, 'case_study_ohi/am_spp_region_sum.csv'))
ohi_rgn_sum   <- read_csv(file.path(dir_git, 'case_study_ohi/ohi_spp_region_sum.csv'))

status_df <- ohi_rgn_sum %>%
  select(rgn_id, ohi_st = status, mean_n_spp) %>%
  mutate(ohi_st = ohi_st) %>%
  full_join(am_rgn_sum   %>% select(rgn_id,    am_st = status), by = 'rgn_id') %>%
  full_join(iucn_rgn_sum %>% select(rgn_id, iucn_st = status), by = 'rgn_id') %>%
  mutate(diff_am   = am_st - ohi_st ,
         diff_iucn = iucn_st - ohi_st) %>%
  gather(scenario, diff, diff_am:diff_iucn)

@@

  geom_hline(yintercept = 0, color = 'gray50', size = .5) +
  geom_violin(fill = 'grey80', alpha = .5,
              scale = 'width',
              draw_quantiles = c(.25, .5, .75)) +
  geom_point(position = position_jitter(w = .3), 
             aes(color = mean_n_spp), alpha = 1, size = 0.25) +
  geom_violin(fill = NA, 
              draw_quantiles = c(.25, .5, .75),
              scale = 'width') +
  labs(x = 'Scenario, compared to OHI 2016',
       y = 'Change in SPP status') +
  scale_x_discrete(labels = c('1. AquaMaps only', 
                              '2. IUCN only'))

### 2016-08-16 coralmaps/coral_maps.Rmd
cleaning out old plots; updating figures; editing manuscript

### 18 species (of 562) have no depth information; one is listed as being dredged from 13 fathoms (~ 25 m)
```

@@

ggsave(plot = coral_area_plot,
       filename = file.path(dir_fig, 'coral_area_plot.png'), device = 'png',
       width = 9, height = 5, units = 'cm', dpi = 600)

@@

### recalc areas and overlaps
iucn_coral_fixed <- spp_coralmaps %>%
  gather(dist, perc, c(sm_perc_raw, sm_perc_shallow)) %>%
  gather(area, ratio, c(area_ratio_raw, area_ratio_shallow)) %>%
  filter(!(str_detect(dist, 'raw') & !(str_detect(area, 'raw')))) %>%
  filter(!(str_detect(dist, 'shallow') & !(str_detect(area, 'shallow')))) %>%
  mutate(method = ifelse(str_detect(dist, 'shallow'), '200 m clip', 'original'))

@@

clipped_quads <- ggplot(iucn_coral_fixed %>%
                      filter(!iucn_sid %in% (iucn_coral_fixed %>% 
                                               filter(perc > 100) %>% 
                                               .$iucn_sid)),
                    aes(x = ratio, y = perc, group = iucn_sid)) +
  ggtheme_plot + 
  ### color the quadrant backgrounds:
  annotate("rect", xmin = 54.5, xmax = 100, ymin = 63, ymax = 100,
           alpha = .3, fill= "#4dac26")  +
  annotate("rect", xmax = 54.5, xmin =   0, ymin = 63, ymax = 100,
           alpha = .3, fill= "#b8e186") +
  annotate("rect", xmin = 54.5, xmax = 100, ymax = 63, ymin =   0,
           alpha = .3, fill= "#f1b6da") +
  annotate("rect", xmax = 54.5, xmin =   0, ymax = 63, ymin =   0,
           alpha = .3, fill= "#d01c8b") +
  ### add grid lines
  geom_vline(xintercept = break_nums, size = 0.25, color = 'white', alpha = .5) +
  geom_hline(yintercept = break_nums, size = 0.25, color = 'white', alpha = .5) +

@@

ggsave(plot = clipped_quads,
       filename = file.path(dir_fig, 'scatter_quadmap_corals.png'), device = 'png',
       width = 17.8, height = 9, units = 'cm', dpi = 600)

@@

>>>>

### 18 species (of 562) have no depth information; one is listed as being dredged from 13 fathoms (~ 25 m)
quantile(spp_depth$max_depth, seq(.9, 1, .01), na.rm = TRUE)
 #   90%    91%    92%    93%    94%    95%    96%    97%    98%    99%   100% 
 # 40.00  44.65  50.00  50.00  50.00  61.25  70.80  78.20  84.10 100.00 200.00

spp_d1 <- spp_depth %>% filter(iucn_sid %in% coral_cells_iucn$iucn_sid) ### mapped spp only
quantile(spp_d1$max_depth, seq(.9, 1, .01), na.rm = TRUE)
 #   90%    91%    92%    93%    94%    95%    96%    97%    98%    99%   100% 
 # 40.00  45.00  50.00  50.00  50.00  54.60  70.00  75.56  82.12 100.00 152.00

@@

ggsave(plot = coral_area_plot,
       filename = file.path(dir_fig, 'fig3a_coral_area_plot.png'), device = 'png',
       width = 9, height = 5, units = 'cm', dpi = 600)

@@

### recalc areas and overlaps
iucn_coral_fixed <- spp_coralmaps %>%
  gather(dist, d_perc, c(sm_perc_raw, sm_perc_shallow)) %>%
  gather(area, a_ratio, c(area_ratio_raw, area_ratio_shallow)) %>%
  filter(!(str_detect(dist, 'raw') & !(str_detect(area, 'raw')))) %>%
  filter(!(str_detect(dist, 'shallow') & !(str_detect(area, 'shallow')))) %>%
  mutate(method = ifelse(str_detect(dist, 'shallow'), '200 m clip', 'original'))

write_csv(iucn_coral_fixed, file.path(dir_git, 'coralmaps', 'iucn_coral_fixed.csv'))

@@

### Plot the new quad graph
clipped_quads <- ggplot(iucn_coral_fixed %>%
                      filter(!iucn_sid %in% (iucn_coral_fixed %>% 
                                               filter(perc > 100) %>% 
                                               .$iucn_sid)),
                    aes(x = a_ratio, y = d_perc, group = iucn_sid)) +
  ggtheme_plot + 
  ### color the quadrant backgrounds:
  annotate("rect", xmin = 54.5, xmax = 100, ymin = 63, ymax = 100,
           alpha = .3, fill= "#4dac26")  +
  annotate("rect", xmax = 54.5, xmin =   0, ymin = 63, ymax = 100,
           alpha = .3, fill= "#b8e186") +
  annotate("rect", xmin = 54.5, xmax = 100, ymax = 63, ymin =   0,
           alpha = .3, fill= "#f1b6da") +
  annotate("rect", xmax = 54.5, xmin =   0, ymax = 63, ymin =   0,
           alpha = .3, fill= "#d01c8b") +
  ### add grid lines
  geom_vline(xintercept = break_nums, size = 0.25, color = 'white', alpha = .5) +
  geom_hline(yintercept = break_nums, size = 0.25, color = 'white', alpha = .5) +

@@

ggsave(plot = clipped_quads,
       filename = file.path(dir_fig, 'fig3b_scatter_quadmap_corals.png'), device = 'png',
       width = 17.8, height = 9, units = 'cm', dpi = 600)

@@

``` {r examine_coral_quartiles, echo = FALSE, eval = TRUE}

iucn_coral_fixed <- read_csv(file.path(dir_git, 'coralmaps', 'iucn_coral_fixed.csv'))

### identify quads based on original breaks from data_explore.Rmd

area_align_mean <- 54.53334
dist_align_mean <- 62.98212

# iucn_sid  am_sid  sciname  area_am  area_iucn_shallow  area_overlap_shallow  sm_range_shallow  area_iucn_raw
# area_overlap_raw  sm_range_raw  dist  perc  area  ratio  method

iucn_coral_quads <- iucn_coral_fixed %>%
  select(iucn_sid, sciname, d_perc, a_ratio, method) %>% ### ditch am_sid, b/c duplicates
  distinct() %>%
  mutate(quad = 'q1',
         quad = ifelse(a_ratio < area_align_mean  & d_perc >= dist_align_mean, 'q2', quad),
         quad = ifelse(a_ratio >= area_align_mean & d_perc < dist_align_mean,  'q3', quad),
         quad = ifelse(a_ratio < area_align_mean  & d_perc < dist_align_mean,  'q4', quad)) %>%
  group_by(method) %>%
  mutate(n_total = n()) %>%
  group_by(method, quad) %>%
  mutate(n_quad = n(),
         pct_quad = n_quad/n_total) %>%
  ungroup()

quad_names <- data.frame('quad' = c('q1', 'q2', 'q3', 'q4'),
                         'quad_name' = factor(c('well-matched', 'dist-matched', 
                                                'area-matched', 'poorly matched'),
                                             ordered = TRUE))

iucn_coral_quads <- iucn_coral_quads %>%
  left_join(quad_names, by = 'quad')

write_csv(iucn_coral_quads, file.path(dir_git, 'coralmaps', 'iucn_coral_quads.csv'))

iucn_coral_quad_sum <- read_csv(file.path(dir_git, 'coralmaps', 'iucn_coral_quads.csv')) %>%
  select(method, quad, quad_name, pct_quad) %>%
  distinct()
### Plot the bar chart
barchart_coral_quads <- ggplot(iucn_coral_quad_sum, 
                                aes(x = method, fill = quad, weight = pct_quad)) +
  ggtheme_plot + 
  theme(panel.grid.major.y = element_blank()) +
  geom_bar(stat = 'count', alpha = 1) +
  scale_fill_manual(values = c('q4' = '#d01c8b', 
                               'q3' = '#f1b6da', 
                               'q2' = '#b8e186',
                               'q1' = '#4dac26'),
                    labels = quad_names$quad_name) +
  scale_y_continuous(expand = c(0, 0), 
                     limits = c(0, 1.1),
                     breaks = break_nums/100,
                     labels = sprintf('%s%%', break_nums)) + 
  ### add grid lines; horizontal but then get flipped
  geom_hline(yintercept = break_nums/100, size = 0.25, color = 'white', alpha = .5) +
  coord_flip() +
  labs(x = 'Taxonomic Group', 
       y = 'Percent of corals by quadrant', 
       fill = 'Alignment')

print(barchart_coral_quads)

ggsave(plot = barchart_coral_quads,
       filename = file.path(dir_fig, 'fig3c_barchart_coral_quads.png'),
       width = 17.8, height = 4, units = 'cm', dpi = 600)

write_csv(iucn_coral_quad_sum, file.path(dir_git, 'coralmaps', 'iucn_coral_quad_sum.csv'))

### 2016-08-16 ms_2_methods.Rmd
cleaning out old plots; updating figures; editing manuscript

___short paragraph about other datasets we didn't include, i.e. SAUP?___

___should this go in the discussion?___
_The methodologies behind the creation of these datasets imply differences in prediction of species distribution due to errors of commission (falsely indicating species presence) and omission (falsely indicating species absence).  Geographic range data such as IUCN range maps frequently introduce commission errors, while species distribution models such as AquaMaps will likely introduce fewer commission errors but more omission errors.  Each type of error bears different implications for conservation goals: commission errors can result in prioritizing areas not relevant to conservation goals, while omission errors may result in protected area networks that fail to include important habitat and range [@rondinini_tradeoffs_2006].  By comparing maps resulting from IUCN and AquaMaps methodologies, we can identify and possibly address mechanistic causes for each type of error._

@@

Overlaying paired distribution maps for a given species, we defined and calculated _distribution alignment_ and _area ratio_ and plotted these in Fig. 2A:

@@

_Distribution alignment - overlap as proxy for common understanding; use Bayesian argument to show that these areas are high-confidence areas; area ratio as proxy for errors of commission/omission.  While we cannot know which dataset is closer to the "truth" we can make inferences based on expectations of EOO and AOO maps - is AquaMaps AOO?_

@@

Noting that a large proportion of corals were identified in the upper-left quadrant, we examined a handful of IUCN coral maps and found that each predicted coral presence in far deeper waters than would be expected based on the IUCN's habitat description.  Using the IUCN's API [REF] to find life history information for all IUCN-mapped corals, we found that none of the paired-map corals is described as occurring deeper than 200 m; 94% are noted as being limited to 50 m or shallower.  We created a 200 m bathymetry raster from Natural Earth's 200 m bathymetry polygon [@natural_earth_XXX] ___(Fig. SXXX)___ and masked our IUCN coral rasters to exclude presence below 200 m.  The resulting maps were again compared to the AquaMaps rasters; ___Fig. XXXX___ plots shifts in coral species alignment due to this depth clipping. ___does some of this belong in the results/discussion?___

@@

_To highlight the differences in the datasets, we recalculated the OHI SPP status values using only one complete dataset at a time.  For the AquaMaps dataset, we used a presence threshold of 0% to align with the OHI 2016 assessment._  ___Fig. 3 compares these single-dataset scores to the 2016 OHI SPP status values.___

_To highlight the differences in the datasets, we selected the subset of species whose ranges are represented in both datasets, eliminating species found in only one or the other dataset.  In the original OHI SPP analysis, IUCN data was used to determine ranges for these overlapping species; we calculated all regional SPP status scores for just these species as our baseline.  We then recalculated the scores using AquaMaps ranges at a 40% presence threshold (as used in the original OHI analysis) and a 0% threshold (to better simulate the "limits of distribution" defined by IUCN maps) and compared them to our IUCN baseline._

_We then modified the original OHI source code to recalculate the 2015 SPP status scores for all regions and all species to examine the effects of changing the AquaMaps presence threshold from 40% to 0% (all range included), and the effects of changing the data source for the overlapping species from IUCN to AquaMaps.  We calculated the differences between these results and the published SPP status scores for 2015._

>>>>

___short paragraph about other datasets we didn't include, i.e. SAUP? BOTW?___

@@

Overlaying paired distribution maps for each species, we defined and calculated _distribution alignment_ and _area ratio_ and plotted these in Fig. 2A:

@@

_Distribution alignment uses overlapping predictions of presence as means of identifying areas of high confidence.  Area ratio provides a proxy for frequency of commission and/or omission errors._

@@

_Based on the results of the map alignment analysis, we chose to examine the effect of explicitly restricting IUCN ranges to depths based on species' life histories.  We selected corals as a case study, due to their foundational role in biodiverse habitats, as well as their lack of mobility and general reliance on photosynthesis._  Using the IUCN's API [REF] to find life history information for all IUCN-mapped corals, we found that none of the paired-map corals is described as occurring deeper than 200 m; 94% are noted as being limited to 50 m or shallower.  We created a 200 m bathymetry raster from Natural Earth's 200 m bathymetry polygon [@natural_earth_XXX] ___(Fig. SXXX)___ and masked our IUCN coral rasters to exclude presence below 200 m.  The resulting maps were again compared to the AquaMaps rasters; ___Fig. XXXX___ plots shifts in coral species alignment due to this depth clipping.

@@

_To highlight the differences in the datasets, we recalculated the OHI SPP status values using only one complete dataset at a time.  For the AquaMaps dataset, we used a presence threshold of 0% to align with the OHI 2016 assessment. Fig. 3 compares these single-dataset scores to the 2016 OHI SPP status values.  While the full OHI 2016 assessment includes the Birds of the World dataset [@REF???] in addition to IUCN and AquaMaps, we omitted it from our calculations for simplicity._

~To highlight the differences in the datasets, we selected the subset of species whose ranges are represented in both datasets, eliminating species found in only one or the other dataset.  In the original OHI SPP analysis, IUCN data was used to determine ranges for these overlapping species; we calculated all regional SPP status scores for just these species as our baseline.  We then recalculated the scores using AquaMaps ranges at a 40% presence threshold (as used in the original OHI analysis) and a 0% threshold (to better simulate the "limits of distribution" defined by IUCN maps) and compared them to our IUCN baseline.~

~We then modified the original OHI source code to recalculate the 2015 SPP status scores for all regions and all species to examine the effects of changing the AquaMaps presence threshold from 40% to 0% (all range included), and the effects of changing the data source for the overlapping species from IUCN to AquaMaps.  We calculated the differences between these results and the published SPP status scores for 2015.~
